Numerical error propagation in the HCP structural pre-processing pipelines

### 2018-04-25 paper.tex

Figure~\ref{fig:iterations} illustrates this iterative process on the previous
exemplar pipeline.

\todo{Explain how graphs are represented.}

>>>>

\begin{figure}
  \includegraphics[scale=0.3]{images/iterative_modif}
  \caption{iteration of proposed modification.}
  \label{fig:iterations}
\end{figure}

Figure~\ref{fig:iterations} illustrates the modification process iteratively in three steps for the previous example.
 Processes that created errors are shown in red, processes that removed errors are in blue,
 yellow nodes are the processes which propagate errors, and other processes are in green.
 For instance, in step one after correcting bet process, fslmaths is recognized as a red process in the next step.
In fact, the created graph in a real pipeline execution is much more complex. 
To simplicity of intricate graph and tracing processes comprehensible, 
the original graph compacted to several subgraphs using a compression technique. 
The compression technique will apply, (1) build subgraphs for every interesting node (e.g. red and blue nodes with their children)
 (2) remove the interesting nodes from graph (3) finding largest connected components in the remaining nodes (iteratively).
